On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-04-27 paper_lap/JCP_response1/response.tex

\qb
\todo{MR}

\qa
7) p. 19. Even for a problem with 22k dofs, 105 iterations of a Krylov method seems like a lot, especially if the problem is well-conditioned. I can?t help but wonder if this is an artifact of the fact that your FMM tolerance is the same as your iterative method tolerance. If you set the latter to 1e-14 or 1e-13, does the number of iterations decrease drastically?

\qb
\todo{MR}

\qa
8) 
p. 21-22. I find the content of Appendix B difficult to understand for a number of reasons. The motivation for such a result is clear, but I'm not sure I totally understand the conclusion. In particular, you want to show that using the adjoint discretization one can interpolate the density on a panel far from the corner. That makes sense. Your approach to showing this is to use the relation (B.1) to find another equivalent integral equation, which you then show can be solved using existing information accurately.
Is the claim that to actually interpolate the density on such a panel, one would need to solve another Dirichlet problem, and it does NOT suffice to just interpolate the value of $\sigma$ obtained on the GL nodes when solving the original problem? Please clarify this point.

There are these other issues I?m having with it:
(a) On your assumptions about the discretization, 1 and 3 have an easy-to-understand interpretation. It's unclear to me what 2 is really assuming about the discretization, given that it seems to mostly to be introducing notation. Of course, I can imagine conditions where $\rho_{0}$ is less than the width of some panels, but is there some deeper restriction?
(b) Your assumption that $\rho_{0}>1$ and your later statement that the rate at which a polynomial interpolant will converge is $C \rho_{0}^{M}$ is a bit awkward, since these choices are specific for a function
on an interval of length 2.
(c) The second paragraph on p. 22 is very unclear to me. I don?t even understand the first sentence as to why k(s,t) would be identically 0 on the same segment as $\gamma([s1,s2])$, or what is really even meant by ?segment? here. Furthermore, it is mentioned that k(s, t) when considered as a function of $t \in \mathbb{C}$ has a singularity at $\gamma(s)$. Given the current setup wouldn't the singularity be at s? I would recommend rewriting this entire paragraph to be more transparent.

\qb
Thank you for pushing on this. We have rewritten the section completely to address all of the concerns above and feel that the readability now is significantly improved. We have eliminated the assumptions on the geometry completely as it can be confusing and rather reduced it to an error estimate of a solution to a Dirichlet problem using the same grid.
\qa
Small fixes and typos:

### 2020-04-27 paper_lap/JCP_response1/05apparatus.tex
updating appendix b and cleaning up review comments in response

For a panel $\gamma([s_1,s_2])$ with discretization nodes $x_i,\dots,x_{i+M}$ corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$). Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ . Typically we use 16th order Gauss-Legendre panels and choose their sizes so that their length is no more than their distance to the nearest corner. This latter choice guarantees that for any $\epsilon>0$ there exists an $M$ such that if the Gauss-Legendre panels are discretized using an $M$-point Gauss-Legendre rule then the density on that panel can be interpolated to relative precision $\epsilon$ in an $L^2$-sense.
(We discuss a sketch of a proof in~\cref{sec:appb})

>>>>

For a panel $\gamma([s_1,s_2])$ with discretization nodes $x_i,\dots,x_{i+M-1}$ corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$). Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ . Typically we use 16th order Gauss-Legendre panels and choose their sizes so that their length is no more than their distance to the nearest corner. This latter choice guarantees that for any $\epsilon>0$ there exists an $M$ such that if the Gauss-Legendre panels are discretized using an $M$-point Gauss-Legendre rule then the density on that panel can be interpolated to relative precision $\epsilon$ in an $L^2$-sense.
(We discuss a sketch of a proof in~\cref{sec:appb})

### 2020-04-27 paper_lap/JCP_response1/manuscript.tex
updating appendix b and cleaning up review comments in response

@@

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
In this section, we demonstrate that for a panel which is sufficiently far from the corner and  discretized using $M$ Gauss-Legendre nodes, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [0,L]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary.
Assume that the discretization satisfies the following assumptions:
\begin{enumerate}
\item All panels which are not at a corner, are separated from the closest corner by at least their panel length.
\item Let $E_{\rho}(\Gamma_{i})$ denote the Bernstein $\rho-$ellipse (see \cite{tref_approx}) corresponding to the panel $\Gamma_{i}$, and let $\rho_{i}$ 
be such that $E_{\rho_{i}}(\Gamma_{i})$ does not intersect $\Gamma \setminus S_{\Gamma_{i}}$, where 
$S_{\Gamma_{i}}$ is the edge containing $\Gamma_{i}$ (see~\cref{fig:illus-cons}). Let $\rho_{0} = \min_{i} \rho_{i} >1$.
\item All panels which are not adjacent to a panel at the corner, are separated from the corner by $2r_{c}$ where $r_{c}$ 
denotes the length of the panel at the corner.
\end{enumerate}
Under these assumptions, it can be shown that the accuracy of computing the
Legendre coefficients of the density (at panels which are not adjacent to a corner panel) for the Neumann problem using the adjoint discretization is related to the accuracy 
in the computation of the solution to an associated Dirichlet problem.
\begin{figure}
\begin{center}
\includegraphics[width=0.3\linewidth]{paper-figs/geom-restriction-illus}
\caption{Illustrative figure for demonstrating constraints required on the geometry discretization. The panel $\Gamma_{i}$ satisfies restriction 1 if $L_{i}/L_{0}>1$. Panel $\Gamma_{j}$ illustrates the largest Bernstein ellipse which intersects the other edges, and Panel $\Gamma_{k}$ illustrates restriction 3 if $r_{k}>2r_{c}$. }
\label{fig:illus-cons}
\end{center}
\end{figure}

Let $A$ denote the operator corresponding to interior Dirichlet problem using a double layer potential. Let $g$ denote the
right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution. Let $f$ be a Legendre polynomial of
degree $n$ scaled to the panel $\gamma([s_{1},s_{2}])$ and $0$ everywhere else. Then
\begin{equation}
\left<\sigma, f \right> = \left< (A^{T})^{-1} g, f\right> = \left< g, A^{-1} f \right> = \langle g, \sigma_{f}\rangle \, ,
\end{equation}
where $\sigma_{f}$ is the solution of the interior Dirichlet problem with boundary data $f$ using a double layer potential.

Using~\cref{lem_adjm}, the above statement implies that the error in computing the $M$ Legendre coefficients of
the density for the Neumann problem is the same as the error in computing the solution of a Dirichlet problem with 
data given by a Legendre polynomial on the same panel.

Let $V$ denote the collection of corner points in parameter space $[0,L]$, i.e. $a \in V$ if $\gamma(a)$ is a corner vertex.
Recall that $\sigma_{f}$ denotes the solution of the Dirichlet problem with boundary data $f$, i.e., 
$\sigma_{f}$ satisfies
\begin{equation}
-\frac{\sigma_{f}(s)}{2}   + \int_{0}^{L} k(s,t) \sigma_{f}(t) dt  = f(s) \,  \quad s\in[0,L]\setminus{V}.
\end{equation}
 Then $\sigma_{f} = -2f + \tilde{\sigma}$ where $\tilde{\sigma}$ satisfies the integral equation
 \begin{equation}
-\frac{\tilde{\sigma}}{2}+ \int_{0}^{L} k(s,t) \tilde{\sigma}(t) dt = -2\int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , \quad s\in[0,L] \setminus V \, ,
 \end{equation}
i.e, $\tilde{\sigma}$ is the solution of the Dirichlet with data $\tilde{f}$ given by
\begin{equation}
\tilde{f}(s) = -2\int_{s_{1}}^{s_{2}} k(s,t) f(t) dt \, , s \in [0,L] \setminus V \, .
\end{equation}
There are two concerns which must be addressed. First, the accuracy of computing $\tilde{f}(s)$ 
for any point $s \in [0,L]$ using an $M$ point Gauss-Legendre quadrature on $[s_{1},s_{2}]$, and secondly, 
the resolution of the function $\tilde{f}(s)$ on the given discretization of the boundary.

For any $s$ which is contained on the same segment as $\gamma([s_{1},s_{2}])$, the kernel $k(s,t)$ is identically $0$.
Thus the boundary data $\tilde{f}(s)=0$  on the same edge as the panel $\gamma([s_{1},s_{2}])$. 
We further observe that $f(t)$ is an entire function when extended to the complex plane, since it is a Legendre polynomial.
Moreover, the nearest singularity of the function $k(s,t)$ in the complex plane as a function of $t$ is at $\gamma(s)$.
From assumption 2, it follows that
the error in computing $\tilde{f}(s)$ using an $M$ point Gauss-Legendre rule is bounded by $C \rho_{0}^{-M}$, where
the constant $C$ is related to the smoothness of $k(s,t)$ as a function of $t \in \mathbb{C}.$
Thus the function $\tilde{f}(s)$ can be computed to any desired precision by increasing the order of quadrature nodes
used to compute the integrals.

With regards to the resolution of the of the function $\tilde{f}(s)$ on the given discretization of the boundary, 
we note that the closest singularity of the function $\tilde{f}(s)$ when restricted to a panel away from the corner
and not on the same edge as $\gamma([s_{1},s_{2}])$ is the closest point on the panel $\gamma([s_{1},s_{2}])$. 
However, by assumption 2, the error in resolving the function $\tilde{f}(s)$ using an $M$ point Gauss-Legendre
or Chebyshev panel is bounded by $C \rho_{0}^{-M}$. Note that the behavior of $\tilde{f}(s)$ in the complex plane is related
to the behavior of $k(s,t)$ in the complex $s$ plane and hence the constant $C$ is $O(1)$.
For the panels, at the corner, based on the proof in Appendix A, the error in resolving the function $\tilde{f}(s)$ when
truncated to a Taylor series of order $N$ is less than $C 2^{-N}$, since all points on $\gamma([s_{1},s_{2}])$ are 
well-separated from corners by twice the panel length $r_{c}$. Thus, by making the panels small enough, $\rho$ can be increased arbitrarily to obtain desired tolerances on the boundary data $\tilde{f}(s)$ on the corresponding discretization of the boundary.

 Thus, the boundary data $\tilde{f}(s)$ is piecewise analytic , which can be approximated to any desired tolerance by appropriately reducing the panel sizes. This is the precise setup for which the discretization of the Dirichlet problem is designed to obtain accurate solutions to the density $\tilde{\sigma}$.

>>>>

\newcommand{\uA}{\underline{A}}
\newcommand{\usigma}{\underline{\sigma}}
\newcommand{\uX}{\underline{X}}
\newcommand{\note}[1]{{\color{red} #1}}

@@

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
{\color{blue}
In this section, we demonstrate that for a panel which is sufficiently far from the corner, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [0,L]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary. Suppose that the boundary is discretized using the procedure discussed in~\cref{sec:resolve}. Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$ and the corresponding weights are given by $w_{1}, \ldots w_{N}$.
Let $X = \mathbb{L}^2({\Gamma})$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{Y}$
denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$.
Let $S:X \to \uX$ denote the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
\begin{equation}
S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, .
\end{equation}
Let $P:\underline{X} \to X$ denote the operator mapping the discretized samples to it's piecewise interpolant on the boundary.
Let $\Gamma_{\ell} = \gamma([s_{1},s_{2}])$ denote a panel that does not contain a corner vertex and is discretized with $M$ nodes  $x_{i},x_{i+1},\ldots x_{i+M-1}$.}

\note{Is there a clean way to give an explicit definition of P or it's obvious?}

{\color{blue}
Let $A$ denote operator corresponding to the interior Dirichlet problem where the solution is represented as a double layer potential. Let $\underline{A}$ denote the $N\times N$ matrix corresponding to the discretization of $A$. Let $g$ denote the
right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution.   Let $\underline{\sigma}$ denote the solution of the linear system $\uA^{T} \usigma = S[g]$. Let $h_{i}$, $i=1,2,\ldots M$, denote the scaled Legendre polynomials to the panel $\Gamma_{\ell}$.
The main result of this appendix is to show that under suitable assumptions, that the computed density can be accurately interpolated on $\Gamma_{\ell}$, i.e.  
\begin{equation}
e = \max_{i=1,2\ldots M} |\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX}| < \varepsilon  
\end{equation}

In practice, given boundary data $g$ and a tolerance $\varepsilon$, it is extremely difficult to construct a discretization of the boundary for which the solution to the corresponding integral equation achieves the desired tolerance numerically for a generic $\Gamma$ (even when both the boundary and solution are smooth). 
We instead derive an estimate for $e$ in terms of the error incurred in solving the interior Dirichlet problem for $M$ piecewise smooth boundary functions.

But first, we present a lemma about the accuracy of Gaussian quadrature
\begin{lem}
\label{lem:b1}
Suppose that $p$ is a polynomial of degree less than $M$, then for any function $g$ in $\mathbb{L}^{2}[-1,1]$, then the integral
$\int_{-1}^{1} p \cdot g$ can be computed accurately using Gaussian quadrature of any order greater than or equal to $M$.
As a consequence, For any $g$ in $\mathbb{L}^{2}(\Gamma)$, then 
\begin{equation}
\left<h_{i},g \right>_{X} = \left< S[h_{i}], S[g] \right>_{\uX}
\end{equation}
\end{lem}

Let $V$ denote the collection of corner points in parameter space $[0,L]$, i.e. $a \in V$ if $\gamma(a)$ is a corner vertex.

\begin{lem}
\label{lem:b2}
Let $f_{i}$ be given by
\begin{equation}
f_{i}(s) = -2 \int_{s_{1}}^{s_{2}} k(s,t) h_{i}(t) dt \, , s\in [0,L] \setminus V \, . \label{eq:deff}
\end{equation}
Consider the interior Dirichlet problem with boundary data $f_{i}$, where we represent the solution via a double layer potential with density $\sigma_{D,i}$, i.e. $\sigma_{D,i}$ satisfies the integral equation
\begin{equation}
A[\sigma_{D,i}] = -\sigma_{D,i}/2 + \int_{0}^{L} k(s,t) \sigma_{D,i}(t) dt  = f_{i}(s) \, , s\in [0,L] \setminus V \, . 
\end{equation}
Then,
\begin{equation}
\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX} = 
\left< g, \sigma_{D,i} \right> - \left< S[g], \usigma_{D,i} \right>_{\uX}
\end{equation}
\end{lem}

\begin{proof}
We first note that if $\sigma_{D,h_{i}}$ is the solution to the integral equation
\begin{equation}
A[\sigma_{D,h_{i}}] = -\frac{\sigma_{D,h_{i}}}{2} + \int_{0}^{L} k(s,t) \sigma_{D,h_{i}} dt = h_{i}(s) \, , s \in [0,L] \setminus V \, ,
\end{equation}
then, $\sigma_{D,h_{i}} = -2h_{i} + \sigma_{D,i}$. 
Similarly, the computed solution $\usigma_{D,h_{i}}$ satisfies $\usigma_{D,h_{i}} = -2S[h_{i}] + \usigma_{D,i}$, where
$\underline{A} [\usigma_{D,h_{i}}] = S[h_{i}]$, and $\underline{A}[\usigma_{D,i}] = S[f_{i}]$. The result for $\usigma$ holds since $PS[h_{i}] = h_{i}$, since $h_{i}$ is a polynomial of degree less than $M$ on a Gauss-Legendre panel discretized using $M$ nodes, and since the Nystr\"{o}m discretization of $A$ is interpolatory in nature.

The error in the inner product of the density with $h_{i}$, then is given by
\begin{equation}
\begin{aligned}
\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX} &=
\left< (A^{-1})^{T}g, h_{i} \right>_{X} -  \left< (\underline{A}^{-1})^{T}S[g], S[h_{i}] \right>_{\uX}   \\
&=\left< g, A^{-1}[h_{i}] \right>_{X} -  \left< S[g], \underline{A}^{-1}[S[h_{i}]] \right>_{\uX}   \\
&=\left< g, \sigma_{D,h_{i}} \right>_{X} -  \left< S[g], \usigma_{D,h_{i}} \right>_{\uX}   \\
&=\left< g, -2h_{i} + \sigma_{D,i} \right>_{X} -  \left< S[g], -2S[h_{i}] + \usigma_{D,i} \right>_{\uX}   \, .
\end{aligned}
\end{equation}
The result then follows since $\left<g,h_{i} \right>_{X} = \left<S[g],S[h_{i}] \right>_{\uX}$ (\cref{lem:b1}).
\end{proof}

\Cref{lem:b2} shows that the error in evaluating the inner product of the computed density $\usigma$ with a polynomial on
$\Gamma_{\ell}$ is the same as the error in evaluating the inner product of a computed density for a Dirichlet problem $\usigma_{D,i}$ with boundary data $g$. 
The Dirichlet boundary data $f_{i}$ (\cref{eq:deff}) corresponding to the density $\sigma_{D,i}$ is an analytic function on each of the edges of the polygon. 
The discretization of $A$ of~\cite{hoskins2019numerical} is precisely designed to compute $\sigma_{D,i}$ accurately to any desired tolerance, under sufficient refinement of the discretization. Since $g$ is also a smooth function, given a tolerance $\varepsilon$, there exists a sufficiently fine discretization of the boundary such that
\begin{equation}
\left| \left< g, \sigma_{D,i} \right>_{X} - \left< S[g], \usigma_{D,i} \right>_{\uX} \right| < \varepsilon \, . \label{eq:dest}
\end{equation}
In practice, a discretization with macroscopic panels at the corner, panels not at a corner vertex separated from the corner by their panel length, and which resolves $g$ to precision $\varepsilon$ is often sufficient to guarantee~\cref{eq:dest}. 
\begin{rem}
The size of the panel at the corner needs to be chosen based on the angle formed at the corner---smaller panels for angles closer to $0$ or $2\pi$, in order to resolve the corresponding close to touching interactions.
\end{rem}
}

\note{Do we include a description of the discretization procedure we use in practice?}
